\chapter*{Acknowledgment}
\thispagestyle{empty}
This work is funded by the \textit{Consejo Nacional de Ciencia y Tecnologia -- CONACYT} (the Mexican National Council for Science and Technology).

I extend my sincere gratitude to the University of Bremen, ITEM, and the Studierendenwerk for their support and for providing an excelent environment for academic and professional growth. I would also like to express my appreciation to Mexico and Conacyt for financially supporting my doctorate, and to Germany and the Netherlands for being my welcoming second home during my academic and professional experience.

I am deeply grateful to Prof. Dr. Alberto Garc\'ia-Ortiz, my Ph.D. advisor, for his invaluable guidance and mentorship throughout this journey. His expertise in transforming students into independent researchers has been fundamental to my development. I also extend my thanks to Prof. Dr. Frans Widdershoven for his insightful reviews and contributions to my professional development in industrial research, as well as to the members of the graduation committee for their valuable feedback and suggestions.

My heartfelt thanks go to my colleagues Ardalan Najafi, Amir Najafi, Wanli Yu, Yanqiu Huang, Robert Schmidt, Yizhi Chen, Jinming Sun, and Andreas Beering for their exceptional collaboration, professional support, and brilliant minds. I am also grateful to Prof. Dr. Karl-Ludwig Krieger, Prof. Dr. Klaus Pawelzik, and Dr. David Rotermund for their excellent collaboration and guidance. A special mention to all the students I have supervised, whose engagement and curiosity enriched my doctoral journey. I appreciate the kind and professional assistance of Kerstin Janssen and Peter Lutzen in the research department. And I am thankful to Tovalin, Julian Rosales, Fernando De la Torre, Ulises Ponce, Carlos Cruz, and Kai M\"uller for their inspiration and support.

On a personal note, I extend my deepest thanks to Atena Berhang and her family for their constant and heartwarming support. I am forever grateful to my parents for their encouragement and teachings of virtue and universal love, and to my brothers Kevin and Efren, my greatest sages and friends. I want to express my infinite love and gratitude to my daughter, Estefania, and my mother, who have been my infinite sources of power. My gratitude also goes to all my family members and friends who have supported me with their good wishes throughout my doctorate. 

Finally, I would like to express my appreciation to Marcus Aurelius, Epictetus, Seneca, and Nezahualc\'oyotl for their philosophical mentorship and inspiration. I want to express my infinite and eternal love and gratitude to the universe for making this research possible.

Yarib Nevarez

The Netherlands, May 2024.

